Branching Random Walk and Probability Problems from Physics and Biology

### 2020-05-27 dissertation/pretext.tex
working on a new template for thesis.

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
presented on June 8, 2020
\vspace{1.0cm}

\justify{}
Title: \underline{Advancing renewable gas storage using flat-histogram methods}.
\vspace{2.0cm}

@@

\begin{center}
Advancing renewable gas storage using flat-histogram methods

@@

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Chair of the Department of Physics
\vspace{1.0cm}
\end{flushleft}

>>>>

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
\nobreak presented on \underline{June 8, 2020}
\vspace{1.0cm}

\justify{}
Title: \underline{Advancing Renewable Gas Storage using Flat-histogram Methods}.
\vspace{2.0cm}

@@

\begin{center}
Advancing Renewable Gas Storage using Flat-histogram Methods

@@

\justify{}
\underline{\hspace{15cm}}
\begin{flushleft}
Head of the Department of Physics
\vspace{1.0cm}
\end{flushleft}
